### 2017-12-01 Body/Section1.tex
rasp

Concrete-filled steel tube (CFST) members have been increasingly used in practical design throughout the globe, as it is recognized that such combination of concrete and steel is generally more efficient and economical seismic-resistant solution, in comparison with, for example, reinforced concrete members. The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation, while the steel tube may allow for the development of confinement effects on the concrete core, thus benefiting both the capacity and ductility of CFSTs.

>>>>

Concrete-filled steel tube (CFST) members have been increasingly used in practical design throughout the globe, as it is recognized that such combination of concrete and steel is generally more efficient and economical seismic-resistant solution, in comparison with, for example, reinforced concrete members (Morino). The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved. Besides the ductility, the composition of concrete and steel will also cause both of the two components under multi-axial stress state and thus, leads to the material properties change. Regarding the concrete core, the steel tube provides the confined stress to it and make it under tri-axial stress state. The strength and ductility of concrete are enhanced by the confinement effects.
